Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-03-15 draft.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass. Error bars are the same as Fig. \ref{fig:rate_raw}. SDSS data (orange squares) are taken from \citet{Graur2013}. The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:snum}
\end{figure}
By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$. We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin. The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}). For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF. For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ from Eqs. \ref{eq:corr_SN} and \ref{eq:corr_G} respectively.

@@

An alternative view on how the SN Ia rate relates to environment can be gained by calculating the rate of SNe per year per unit stellar mass: SNuM. A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin. We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$ and at $z\sim0$ in LOSS as presented in \citet{Li2011a}. We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}. Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data. While the data from LOSS and SDSS lies slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method. Any true difference between predicted and observed SNuM could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
\section{The delay-time distribution as a function of supernova properties}
\label{sec:split_x1_c}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass. Error bars are the same as Fig. \ref{fig:rate_raw}. Literature data are that from SDSS spectra (orange squares; \citealt{Graur2013}) and the LOSS sample (grey dotted; \citealt{Li2011a}). The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the  prediction of the model using our best fit DTD from Section \ref{subsec:results_dtd} (coloured curves). }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:snum}
\end{figure}
By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$. We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin. The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}). For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF. For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ from Eqs. \ref{eq:corr_SN} and \ref{eq:corr_G} respectively.

@@

An alternative view on how the SN Ia rate relates to environment can be gained by calculating the rate of SNe per year per unit stellar mass: SNuM. A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin. We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$ and at $z\sim0$ in LOSS as presented in \citet{Li2011a}. We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}. Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data. While the data from LOSS and SDSS spectra lie slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method. Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
\section{The delay-time distribution as a function of supernova properties}
\label{sec:split_x1_c}
